---
title: "Week 2 Task 3 Questions"
author: "Ken Harmon"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:  
    keep_md: true
    toc: true
    toc_float: true
    code_folding: hide
    fig_height: 6
    fig_width: 12
    fig_align: 'center'
---

```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_libraries, include=FALSE}
# Use this R-Chunk to load all your libraries!
#install.packages("tidyverse") # run this line once in console to get package
library(tidyverse)

```

```{r load_data}
# Use this R-Chunk to import all your datasets!

```

## Background

[ ] Take notes on your reading of the specified ‘R for Data Science’ chapter in the README.md or in a ‘.R’ script in the class task folder
[ ] Develop a few novel questions that data can answer
[ ] Get feedback from 5-10 people on their interest in your questions and summarize this feedback
[ ] Find other examples of people addressing your question
[ ] Present your question to a data scientist to get feedback on the quality of the question and if it can be addressed in 2-months.
[ ] Create one .rmd file that has your report
[ ] Have a section for each question
[ ] Push your .Rmd, .md, and .html to your GitHub repo

## Question one

The world has different fertility (birth rates) per country. I assume that this can be attributed to many factors. THe United States is about as ethically diverse as any country in the world. 

Is there a correlation of fertility rates between ethnicities within the United States and the countries where those enthnicities originate?

https://www.unomaha.edu/college-of-public-affairs-and-community-service/center-for-public-affairs-research/news/fertility-rate-gap.php

https://ifstudies.org/blog/baby-bust-fertility-is-declining-the-most-among-minority-women

## Question two

If there is a difference between ethnicities' fertility rates within the United States what are the project growth rates and total population within the United States?

https://ifstudies.org/blog/baby-bust-fertility-is-declining-the-most-among-minority-women

## Question three

Are cancer rates increasing or are we just living longer?
How do Cancer rates relate to life expectancy over time or by country?

https://scienceblog.cancerresearchuk.org/2015/02/04/why-are-cancer-rates-increasing/

https://www.livescience.com/51099-the-three-reasons-cancer-rates-are-rising.html

## Question four

Is there a statistic of an NCAA basketball team that can help me predict how well they will do in th March Madness tournament?

https://www.dratings.com/predictor/bracketology/


