---
title: "Table of Contents"
output: 
  html_document:
    theme: cerulean
    code_folding: hide

---
```{r, include=FALSE}
library(tidyverse)
```

## Assignments {.tabset .tabset-fade}

### Week 1{.tabset .tabset-fade}

#### Rauser

The rendered document is available on rpubs at [http://rpubs.com/jrauser/hhsd_notes](http://rpubs.com/jrauser/hhsd_notes).

Cleveland's three visual operations of pattern perception

1. Detection (geometric shape encodes data)
    a. Larger the proportional difference is easier to detect
    b. banking to 45

2. Assembly
    a. reification (parts of a whole)
    b. emergence
    c. Law of Closure
    d. Law of Continuity
    e. Law of Similarity

3. Estimation
    a. discrimination
    b. ranking
    c. ratio-ing
    
Ranking of Encoding

1. position along a common scale
2. position on identical but nonaligned scales
3. length
4. Slope
5. Area
6. Volume, Density, or Color Saturatiom
7. Color Hue (categorical)

#### Day 01

[Good Data Scientist](https://towardsdatascience.com/what-makes-a-good-data-scientist-engineer-a8b4d7948a86)

Alt +- 
Alt shift k
CTL Shift m
CTRL ALT i

#### Task 2

[Google R Style Guide](https://google.github.io/styleguide/Rguide.xml)
[335 Website](https://byuistats.github.io/M335/)
[Stack Overflow](https://stackoverflow.com/) Login: harmonk Password:
[Slack.com](https://byuidwv.slack.com)
[Github](https://github.com/) Login: harmkenn (harmonke@byui.com) Pasword: 1qw32!QW#@
[Linkedin](https://www.linkedin.com/) Login: harmkenn@gmail.com Password: 1qw32!QW#@

### Week 2{.tabset .tabset-fade}

#### Readings

##### Being Readings

o Effectively Communicating Numbers (pg 1-13)

This process consists of the following six fundamental stages:

  1. Determine your message and identify the data necessary to communicate it.
  2. Determine if a table, graph, or combination of both is needed to communicate your message.
  The remaining stages apply only if one or more graphs are required.
  3. Determine the best means to encode the values.
  4. Determine where to display each variable.
  5. Determine the best design for the remaining objects.
  6. Determine if particular data should be featured above the rest, and if so, how.

Categorical: Nomial, Ordinal, Interval

Graphs

  1. Time Series
  2. Ranking Relationships
  3. Part to Whole
  4. Deviation Relationships
  5. Distribution relationships
  6. Correlation
  7. Nominal

Avoid Area or Volume relationship: Linear is best

o Hans Rosling: The best stats you’ve ever seen

  1. Aggrigate vs deaggrigated data
  2. Time and bubble trends
  3. gapminder
  4. Make data available
  5. Log scales to make it look linear
  
o Questions and best data science

  1. Ask questions that matter
  2. Know when the question has been answered logically
  3. Know when the question has been answered creativally
      test your solution and try to make it fail

##### Doing Readings

o Chapter 3: R for Data Science - Data visualization

###### 3.1 Introduction 

###### 3.1.1 Prerequisites

###### 3.2 First Steps

###### 3.2.2 Creating  a ggplot

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy), color="blue")
```

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = hwy, y = cyl))
```

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = class, y = drv))
```

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color=class))
```

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color=displ))
```

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color=trans))
```

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = displ, color=trans))
```

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = displ, color=displ<5))
```

###### 3.5 Facets

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
```

###### 3.5.1 

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)
```

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```

###### 3.6 Geometric

```{r}
ggplot(data = mpg) + 
  geom_smooth(mapping = aes(x = displ, y = hwy))
```

```{r}
ggplot(data = mpg) + 
  geom_smooth(mapping = aes(x = displ, y = hwy, linetype = drv))
```

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  geom_smooth(mapping = aes(x = displ, y = hwy))
```

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()
```

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = class)) + 
  geom_smooth(data = filter(mpg, class == "subcompact"), se = FALSE)
```

###### 3.6.1 Geometric Exercises 

########### 1

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + geom_line() + geom_point()
```

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + geom_boxplot()
```

```{r}
ggplot(data = mpg, mapping = aes(x = displ)) + geom_histogram()
```

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + geom_area()
```

########### 2
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

########### 6
```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth(mapping = aes(x = displ, y = hwy, class = drv), se = FALSE)
```

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(mapping = aes(x = displ, y = hwy, class = drv), se = FALSE)
```

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_smooth(se = FALSE)
```

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(mapping = aes(x = displ, y = hwy, linetype = drv), se = FALSE)
```

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() 
```

###### 3.7 Statistical Transformation {.tabset .tabset-fade}

###### 3.7 Lesson

```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut))
```

```{r}
demo <- tribble(
  ~cut,         ~freq,
  "Fair",       1610,
  "Good",       4906,
  "Very Good",  12082,
  "Premium",    13791,
  "Ideal",      21551
)

ggplot(data = demo) +
  geom_bar(mapping = aes(x = cut, y = freq), stat = "identity")
```

```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, y = ..prop.., group = 1))
```

```{r}
ggplot(data = diamonds) + 
  stat_summary(
    mapping = aes(x = cut, y = depth),
    fun.ymin = min,
    fun.ymax = max,
    fun.y = median
  )
```

###### 3.7.1 Geometric Exercises 

########### 1

###### 3.8 Position Adjustment {.tabset .tabset-fade}

###### 3.8 Lesson

```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, colour = cut))
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = cut))
```

```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = clarity))
```

```{r}
ggplot(data = diamonds) + 
  geom_bar(alpha = 1/5, mapping = aes(x = cut, fill = clarity), position = "fill")
```

```{r}
ggplot(data = diamonds) + 
  geom_bar(mapping = aes(x = cut, fill = clarity), position = "dodge")
```

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy), position = "jitter")
```

###### 3.9 Coordinate System {.tabset .tabset-fade}

###### 3.9 Lesson

```{r}
ggplot(data = mpg, mapping = aes(x = class, y = hwy)) + 
  geom_boxplot() +
  coord_flip()
```

```{r}
nz <- map_data("nz")
ggplot(nz, aes(long, lat, group = group)) +
  geom_polygon(fill = "white", colour = "black") +
  coord_quickmap()
```
```{r}
bar <- ggplot(data = diamonds) + 
  geom_bar(
    mapping = aes(x = cut, fill = cut), 
    show.legend = FALSE,
    width = 1
  ) + 
  theme(aspect.ratio = 1) +
  labs(x = NULL, y = NULL)

bar + coord_flip()
bar + coord_polar()
```

```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +
  coord_fixed()
```

###### 3.10 Graphics Grammar {.tabset .tabset-fade}

###### 3.10 Lesson

Seven Parameters of Graph
ggplot(data = <DATA>) + 
  <GEOM_FUNCTION>(
     mapping = aes(<MAPPINGS>),
     stat = <STAT>, 
     position = <POSITION>
  ) +
  <COORDINATE_FUNCTION> +
  <FACET_FUNCTION>


o GitHub and Rstudio by Github (stop after the ‘Commit local changes with Git’)


o GitHub for Data Scientists
o Using the R-Studio GUI by R-Studio
o Chapter 8: R for Data Science - Projects
o MCS 335, Git, and Github use
o R-Studio and the Git GUI
o Creating Questions for your project
o Chapter 5: R for Data Science - Data transformation
o DataCamp: 1 Data Wrangling Chapter of Introduction to Tidyverse

```{r}
library(gapminder)
library(dplyr)
gapminder
gapminder %>% filter(year == 1957)
gapminder %>% filter(year == 2002, country =="China")
# Sort in ascending order of lifeExp
gapminder %>% arrange(lifeExp)
# Sort in descending order of lifeExp
gapminder %>% arrange(desc(lifeExp))
# Filter for the year 1957, then arrange in descending order of population
gapminder %>% filter(year == 1957) %>% arrange(desc(pop))
# Use mutate to change lifeExp to be in months
gapminder %>% mutate(lifeExp = 12*lifeExp)
# Use mutate to create a new column called lifeExpMonths
gapminder %>% mutate(lifeExpMonths = 12*lifeExp)
# Filter, mutate, and arrange the gapminder dataset
gapminder %>% filter(year==2007) %>% mutate(lifeExpMonths = 12*lifeExp) %>% arrange(desc(lifeExpMonths))
```
o DataCamp: 2 Data Visualization Chapter of Introduction to Tidyverse

```{r}
library(ggplot2)
gapminder_1952 <- gapminder %>% filter(year == 1952)
# Change to put pop on the x-axis and gdpPercap on the y-axis
ggplot(gapminder_1952, aes(x = pop, y = gdpPercap)) +
  geom_point()
# Create a scatter plot with pop on the x-axis and lifeExp on the y-axis
ggplot(gapminder_1952, aes(x = pop, y = lifeExp)) + geom_point()
# Change this plot to put the x-axis on a log scale
ggplot(gapminder_1952, aes(x = pop, y = lifeExp)) + geom_point() + scale_x_log10()
# Scatter plot comparing pop and gdpPercap, with both axes on a log scale
ggplot(gapminder_1952, aes(x = pop, y = gdpPercap)) + geom_point() + scale_x_log10() + scale_y_log10()
# Scatter plot comparing pop and lifeExp, with color representing continent
ggplot(gapminder_1952, aes(x = pop, y = lifeExp, color = continent)) + geom_point()+ scale_x_log10()
# Add the size aesthetic to represent a country's gdpPercap
ggplot(gapminder_1952, aes(x = pop, y = lifeExp, color = continent, size = gdpPercap)) + geom_point() + scale_x_log10()
# Scatter plot comparing pop and lifeExp, faceted by continent
ggplot(gapminder_1952, aes(x = pop, y = lifeExp)) + geom_point() + scale_x_log10() + facet_wrap(~continent)
# Scatter plot comparing gdpPercap and lifeExp, with color representing continent
# and size representing population, faceted by year
ggplot(gapminder, aes(x = gdpPercap, y = lifeExp, color = continent, size = pop)) + geom_point() + facet_wrap(~year)+ scale_x_log10()
```


o DataCamp: 3 Grouping and Summarizing Chapter of Introduction to Tidyverse

```{r}
gapminder %>% filter(year == 2007) %>% summarize(meanLifeExp = mean(lifeExp), totalPop = sum(pop))
# Summarize to find the median life expectancy
gapminder %>% summarize(medianLifeExp = median(lifeExp))
# Filter for 1957 then summarize the median life expectancy
gapminder %>% filter(year == 1957) %>% summarize(medianLifeExp = median(lifeExp))
# Filter for 1957 then summarize the median life expectancy and the maximum GDP per capita
gapminder %>% filter(year == 1957) %>% summarize(medianLifeExp = median(lifeExp), maxGdpPercap = max(gdpPercap))
gapminder %>% group_by(continent) %>% filter(year == 2007) %>% summarize(meanLifeExp = mean(lifeExp), totalPop = sum(pop))
gapminder
# Find median life expectancy and maximum GDP per capita in each year
gapminder %>% group_by(year) %>% summarize(medianLifeExp = median(lifeExp), maxGdpPercap = max(gdpPercap))
# Find median life expectancy and maximum GDP per capita in each continent in 1957
gapminder %>% filter(year==1957) %>% group_by(continent) %>%summarize(medianLifeExp = median(lifeExp), maxGdpPercap = max(gdpPercap))
# Find median life expectancy and maximum GDP per capita in each year/continent combination
gapminder %>% group_by(continent,year) %>%summarize(medianLifeExp = median(lifeExp), maxGdpPercap = max(gdpPercap))

by_year <- gapminder %>% group_by(year) %>% summarize(medianLifeExp = median(lifeExp), maxGdpPercap = max(gdpPercap))

# Create a scatter plot showing the change in medianLifeExp over time
ggplot(by_year, aes(x=year, y=medianLifeExp)) + geom_point() + expand_limits(y=0)

# Summarize medianGdpPercap within each continent within each year: by_year_continent
by_year_continent <- gapminder %>% group_by(continent,year) %>% summarize(medianGdpPercap = median(gdpPercap))

# Plot the change in medianGdpPercap in each continent over time
ggplot(by_year_continent, aes(x=year, y=medianGdpPercap, color=continent)) + geom_point() + expand_limits(y=0)

# Summarize the median GDP and median life expectancy per continent in 2007
by_continent_2007<-gapminder %>% filter(year == 2007) %>% group_by(continent) %>% summarize(medianLifeExp = median(lifeExp), medianGdpPercap=median(gdpPercap))

# Use a scatter plot to compare the median GDP and median life expectancy
ggplot(by_continent_2007, aes(x=medianGdpPercap, y=medianLifeExp, color=continent)) + geom_point() + expand_limits(y=0)
```

o DataCamp: 4 Line Plots Chapter of Introduction to Tidyverse

```{r}
# Summarize the median gdpPercap by year, then save it as by_year
by_year <- gapminder %>% group_by(year) %>% summarize(medianGdpPercap = median(gdpPercap))

# Create a line plot showing the change in medianGdpPercap over time
ggplot(by_year, aes(x=year, y=medianGdpPercap)) + geom_line() + expand_limits(y=0)

# Summarize the median gdpPercap by year & continent, save as by_year_continent
by_year_continent <- gapminder %>% group_by(year,continent) %>% summarize(medianGdpPercap = median(gdpPercap))

# Create a line plot showing the change in medianGdpPercap by continent over time
ggplot(by_year_continent, aes(x=year, y=medianGdpPercap, color=continent)) + geom_line() + expand_limits(y=0)

# Summarize the median gdpPercap by year and continent in 1952
by_continent <- gapminder %>% group_by(continent) %>% filter(year == 1952) %>% summarize(medianGdpPercap = median(gdpPercap))

# Create a bar plot showing medianGdp by continent
ggplot(by_continent, aes(x=continent, y=medianGdpPercap)) + geom_col()

# Filter for observations in the Oceania continent in 1952
oceania_1952 <- gapminder %>% group_by(country) %>% filter(continent == "Oceania", year == 1952) 

# Create a bar plot of gdpPercap by country
ggplot(oceania_1952, aes(x=country, y=gdpPercap)) + geom_col()

gapminder_1952 <- gapminder %>% filter(year == 1952)

# Create a histogram of population (pop)
ggplot(gapminder_1952, aes(x=pop)) + geom_histogram()

# Create a histogram of population (pop), with x on a log scale
ggplot(gapminder_1952, aes(x=pop)) + geom_histogram() + scale_x_log10()

# Create a boxplot comparing gdpPercap among continents
ggplot(gapminder_1952, aes(x=continent, y=gdpPercap)) + geom_boxplot() + scale_y_log10()

# Add a title to this graph: "Comparing GDP per capita across continents"
ggplot(gapminder_1952, aes(x = continent, y = gdpPercap)) + geom_boxplot() + scale_y_log10() + labs(title ="Comparing GDP per capita across continents")
```


#### Task 3

```{r}

```

### Week 3{.tabset .tabset-fade}

#### t-Test
```{r}

```


#### Wilcoxon
```{r}

```

